%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Cloud Security Engineer} % Job title
    {Tatum Security} % Organization
    {Seoul, S.Korea} % Location
    {Aug. 2023 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Zero Trust Architecture}
        \begin{itemize}
          \item {Research and development of DevSecOps-based cloud security}
          \item {Development of CNCF security project-based solutions using Go}
          \item {Research and development of Zero Trust Segmentation solutions}
          \item {Implemented API visibility and security integration for 'Akamai Guardicore Segmentation' and 'Palo Alto Networks - Prisma Cloud'}
        \end{itemize}
        \item {Cloud Security Solutions}
        \begin{itemize}
          \item {Developed CIEM solution for multi-cloud permission visibility}
          \item {Implemented CSPM for CNAPP targeting AWS, GCP, Azure, NCP, NHN, and KT}
          \item {Enhanced product capabilities through AWS Security Hub Best Practices implementation}
          \item {Automated security compliance for CIS, NIST, DoD, ISO standards}
          \item {Applied Prowler and Powerpipe for financial security compliance automation}
        \end{itemize}
        \item {Infrastructure Security}
        \begin{itemize}
          \item {Researched automated vulnerability diagnosis for VMware ESXi, vSphere, and XenServer}
          \item {Built and operated on-premise environments based on vSphere and Proxmox}
        \end{itemize}
        \item {Patent}
        \begin{itemize}
          \item {Korea, PAT. No. 10-2024-0098442, "Relationship generating device for multiple clouds" (Jul. 2024)}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Security Engineer} % Job title
    {S2W Inc.} % Organization
    {Seongnam-si, S.Korea} % Location
    {Jan. 2022 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gained insights into CTI solutions through cybersecurity data analysis of the dark web}
        \item {Implemented on-premise DevOps CI/CD pipeline and GitOps-based service automation}
        \item {Developed and maintained Elastic Search-based information gathering system}
        \item {Developed Spring Boot based B2G search engine solution backend}
        \item {Korea, PAT. No. 10-2022-0189561, Online Threat Data Saving Server and Method (2022.12.29)}
        \item {Korea, PAT. No. 10-2022-0190122, Threat Data Search Method for Private Channel (2022.12.30)}
        \item {Developed Port Scanner for Attack Surface Management and handled large-scale data processing}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Full-time Master's Student Researcher} % Job title
    {Korea University, Hacking and Countermeasure Research Lab} % Organization
    {Seoul, S.Korea} % Location
    {Feb. 2021 - Dec. 2021} % Date(s)
    {
      \begin{cvitems}
        \item {Published in Journal of Cloud Computing (Sep. 2024)}
        \begin{itemize}
          \item {Domain knowledge free cloud-IDS with lightweight embedding method}
          \item {Authors: Yongsik Kim, *Gunho Park \& Huy Kang Kim}
          \item {DOI: 10.1186/s13677-024-00707-8}
        \end{itemize}
        \item {Research Projects}
        \begin{itemize}
          \item {NLP-based Cyber Threat Intelligence System Research (Samsung SDS, Mar. 2021 - Dec. 2021)}
          \item {Security and Ultra-High Speed Integrity Technology for Next-Generation In-Vehicle Networks (IITP, Apr. 2021 - Dec. 2021)}
          \item {Next-Generation Security R\&D Challenge (IITP, Aug. 2021 - Dec. 2021)}
        \end{itemize}
        \item {Patent: PCT/KR2022/017082}
        \begin{itemize}
          \item {Lightweight Real-Time Anomaly Detection Method Using CAN Message Analysis and Neural Network Model (Nov. 2022)}
        \end{itemize}
        \item {Infrastructure Development}
        \begin{itemize}
          \item {Built and operated vulnerability verification and IDS development competition infrastructure for Automotive Grade Linux (AGL) infotainment systems}
        \end{itemize}
        \item {Received first semester scholarship in 2021 academic year}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Security Engineer} % Job title
    {LSware Inc.} % Organization
    {Seoul, S.Korea} % Location
    {Jun. 2020 - Dec. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Linux ransomware response and recovery automation systems}
        \item {Researched ML-based anomaly detection and anonymous network tracking}
        \item {Published at CISC-W'20: "Automated Backup Linux Kernel Module(LKM) Against Ransomware \& Classification of Grayscale Images for Encrypted File Detection"}
        \item {Published at KSC2020: "A Study on the Malware Classification Using Deep Learning and the Detection of Encrypted Files through the Transformation of Grayscale Images"}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Software Quality Assurance Intern} % Job title
    {LSware Inc.} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2020 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tested security vulnerability diagnostics and access control systems}
        \item {Developed monitoring system and automated consistency check tools}
        \item {Implemented test automation scripts and improved methodologies}
      \end{cvitems}
    }

\end{cventries}