%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Security Mentor} % Affiliation/role
  {WhiteHat School, Korea Information Technology Research Institute (KITRI)} % Organization/group
  {Seoul, S.Korea} % Location
  {Sep. 2023 - Present} % Date(s)
  {
    \begin{cvitems}
      \item {Teaching in next-generation security leader training program organized by Ministry of Science and ICT}
      \begin{itemize}
        \item {VMware \& Hyper-V infrastructure course instructor}
        \item {ELK-based SIEM design and implementation lecturer}
        \item {Kubernetes cluster deployment with kind basic course}
      \end{itemize}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Guest Lecturer} % Affiliation/role
  {Kangwon National University Big Data-Convergence Security Division} % Organization/group
  {Gangwon, S.Korea} % Location
  {Jan. 2024} % Date(s)
  {
    \begin{cvitems}
      \item {Delivered special lecture on Information Security for university students}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Security Product Development Track} % Affiliation/role
  {Best of the Best (BoB)} % Organization/group
  {Geumcheon District, S.Korea} % Location
  {Jun. 2019 - Mar. 2020} % Date(s)
  {
    \begin{cvitems}
      \item {The Cyber Security Talent Development Program, organized by the Ministry of Science and ICT and hosted by the Korea Information Technology Research Institute (KITRI).}
      \item {Conducted POS Vulnerability Analysis \& Security Verification project with Financial Security Agency.}
      \item {Held several hacking competitions as non-profit events.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Development Projects} % Affiliation/role
  {Naver Whale Browser Extensions} % Organization/group
  {S.Korea} % Location
  {2018} % Date(s)
  {
    \begin{cvitems}
      \item {Popular Movies Extension (TMDB)}
      \begin{itemize}
        \item {Developed movie search sidebar extension}
        \item {Rating 4.9/5.0 with 22,083 users and 23,734 downloads (as of Nov. 2024)}
      \end{itemize}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}